Modern Graph Generators: A Survey

### 2018-11-09 challenges.tex
Fixed text to comply with plagiarism requirements

The evolution of graphs can be considered from multiple perspectives. We can assume a static set of nodes and a varying set of edges.  Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items. In the most general case we can assume any changes in both set of nodes and set of edges. Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}. In some graph applications, such as, e.g., social networks, the evolution of the
data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
evolving graphs have further specific features. For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow. Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.

@@

The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases. However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a generator for dealing with this area. In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e. graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges. The generator generates a time series of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., insertion or deletion of an edge or a vertex. The generator keeps track of a (dynamic) ground truth clustering. The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.

>>>>

The evolution of graphs can be considered from multiple perspectives. We can assume a static set of nodes and a varying set of edges.  Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items. In the most general case we can assume any changes in both set of nodes and set of edges. Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}. In some graph applications, such as, e.g., social networks, the evolution of the
data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
evolving graphs have further specific features. For example, some graphs grow
over time according to a \emph{densification power law} which means that in real
graphs, edges tend to appear at a higher pace than vertices, meaning that these
graphs densify as they grow. Also the way the new edges are distributed has the
effect of a shrinking diameter that ends up stabilizing as the graph grows with time.

@@

The respective data generator should hence be able to simulate a natural growth
and/or changes in the structure of the graph with regards to the various
features of distinct use cases. However,  even though the area of dynamic graphs
is intensively studied, surprisingly there seem to exist only very few proposals
of a generator for dealing with this area.
In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering
dynamic graphs}, i.e. graphs where the clustering corresponds to the partition
of nodes into natural groups based on the paradigm of intra-cluster density
versus inter-cluster sparsity of edges. The generator generates a time series
of random graphs $G_0, G_1, ..., G_n$, where $G_t$ emerges from $G_{t-1}$ via
successive atomic updates like for instance, the insertion of a vertex or the removal of an
edge. The generator monitors the (dynamic) ground truth clustering and the probability
of the atomic events is chosen in such a way that the ground truth clustering is
maintained while the randomness of the generated grpah is kept.

### 2018-11-09 data_sets.tex
Fixed text to comply with plagiarism requirements

Besides graph data generators, many graph algorithms and systems are benchmarked using real-world graph data sets, including new graph data generation techniques. In this section, we review the most widely used graph datasets in the literature and their purpose.

@@

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex is a product and an edge between two products
    exists if a person has bought the two products.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges represent the acquitances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges represent their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

@@

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This is a network extracted
      from Wikipedia, where the vertices represent users  and the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompained with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the trust level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: A network of American university
    football teams. Each node represents a football team and the edges represent
    the matches between them during the season. Each team is associated to a
    division.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{DbPedia}~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
    a structured version of Wikipedia. It allows users to semantically query the
    relationships between the different resources at Wikipedia.
  \item \textbf{Freebase}~\cite{bollacker2008freebase}: This is a collaborative knowledge base
    made of metadata that is mainly provided by community members. It contains
    structured data from multiple sources in an attempt to create a global
    resource of information accessible both from persons and machines. The
    project was discontinued in 2014 and replaced by Wikidata.
  \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
    \textbf{Yago3}~\cite{mahdisoltani2013yago3}: These are
    open source knowledge bases developed at the Max Planck Institute of
    Computer Science in Saarbr\"ucken. They contain structured data  that has been automatically extracted
    from Wikipedia and other sources.
  \item \textbf{Wikidata}~\cite{vrandevcic2014wikidata}: This is a knowledge base
    collaboratively edited by the community and hosted by the Wikimedia
    Foundation. It contains structured data from its sister projects Wikipedia,
    Wikivoyage, Wikisource and others.
  \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset
    crawled from different sources, including Freebase, DBPedia or the BBC. A
    detailed description of the crawling process can be found in~\cite{kafer2012towards}.
\end{itemize}

>>>>

Besides graph data generators, many graph algorithms and systems are benchmarked
using real-world graph data sets, including new graph data generation
techniques. In this section, we review those graph datasets most widely used in
the literature and their purpose.

@@

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex represents a product while edges between two products
    exists if a person bought both of them.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquitances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

@@

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This network is extracted
      from Wikipedia and the vertices represent users  while the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompained with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the trust level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: This network represent American university
    football teams. Each node is a football team and the edges are those 
    games between teams during the season. Each team is associated to a
    division.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{DbPedia}~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
    a structured version of Wikipedia. It allows users to semantically query the
    relationships between the different resources at Wikipedia.
  \item \textbf{Freebase}~\cite{bollacker2008freebase}: This is a collaborative knowledge base
    made of metadata maintained by community members. It contains
    structured data from multiple sources in an attempt to create a global
    resource of information accessible both from persons and machines. The
    project was discontinued in 2014 and replaced by Wikidata.
  \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
    \textbf{Yago3}~\cite{mahdisoltani2013yago3}: These are
    open source knowledge bases developed at the Max Planck Institute of
    Computer Science in Saarbr\"ucken. They contain structured data  that has been automatically extracted
    from Wikipedia and other sources.
  \item \textbf{Wikidata}~\cite{vrandevcic2014wikidata}: This is a knowledge base
    collaboratively edited by the community and hosted by the Wikimedia
    Foundation. It contains structured data from other related projects such as Wikipedia,
    Wikivoyage or Wikisource.
  \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset
    crawled from different sources, including Freebase, DBPedia or the BBC. A
    detailed description of the crawling process can be found in~\cite{kafer2012towards}.
\end{itemize}

### 2018-11-09 generators_analytics.tex
Fixed text to comply with plagiarism requirements

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a weighted, directed graph that follows a power-law distribution and four related analysis techniques (namely graph construction, graph extraction with BFS, classification of large vertex sets, and graph analysis with betweenness centrality). The generator has the following parameters: number of vertices, number of edges, and maximum weight of an edge. It outputs a list of tuples containing identifiers of vertices of an edge (with the direction from the first one to the second one) and weights (positive integers  with a uniform random distribution) assigned to the edges of the multigraph.  The algorithm of the generator is based on R-MAT. To avoid data locality, in the final step the vertex numbers are randomly permuted and then the tuples are randomly shuffled. A related project from the same authors developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}. It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2) input graph instances used in the DARPA HPCS SSCA\#2 graph theory benchmark (version 1.0), and (3) small-world graphs based on the R-MAT model.

>>>>

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
weighted, directed graph that follows a power-law distribution and four related
analysis techniques (namely graph construction, graph extraction with BFS,
                     classification of large vertex sets, and graph analysis
                     with betweenness centrality). The generator has the
following parameters: the number of vertices, the number of edges, and maximum weight of
an edge. It outputs a list of tuples containing identifiers of vertices of an
edge (with the direction from the first one to the second one) and weights
(positive integers  with a uniform random distribution) assigned to the edges of
the multigraph.  The algorithm of the generator is based on R-MAT. To reduce the data
locality, the vertex ids are randomly permuted and the output
tuples are shuffled. A related project from the same authors
developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
(version 1.0), and (3) small-world graphs generated using the R-MAT graph
generator.

### 2018-11-09 generators_community_detection.tex
Fixed text to comply with plagiarism requirements

Community detection is one of the many graph analytics algorithms typically used
on domains such as social networks or bioinformatics. Communities are groups of
vertices that are highly connected among them, while being scarcely connected to
the rest of the graph. Such communities emerge from the fact that real graphs
are not random, but follow real-world dynamics that make similar entities to
have a larger probability to be connected. As a consequence, detected
communities are used to reveal vertices with similar characteristics, for
instance to discover functionally equivalent proteins in protein-protein
interaction networks, or persons with similar interests in social networks. Such
applications have made community detection a hot topic during the last fifteen
years with tens of developed algorithms and detection
strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. In order
to compare the quality of the different proposed techniques, one needs graphs
with \emph{reference communities}, that is, communities known beforehand. Since
it is very difficult to have large real graphs with reference communities
(mainly because these would require a manual labeling), graphs for benchmarking
community detection algorithms are typically generated synthetically.

@@

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of different sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which specifies the fraction of
its links connecting nodes belonging to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by obeying the described constraints.

>>>>

Community detection is one of the many graph analytics algorithms typically used
on domains such as social networks or bioinformatics. Communities are groups of
vertices that are highly connected among them, while being scarcely connected to
the rest of the graph. Such communities emerge from the fact that real graphs
are not random, but follow real-world dynamics that make similar entities to
have a larger probability to be connected. As a consequence, detected
communities are used to reveal vertices with similar characteristics, for
instance to discover functionally equivalent proteins in protein-protein
interaction networks, or persons with similar interests in social networks. Such
applications have made community detection a hot topic during the last fifteen
years with tens of developed algorithms and detection
strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
comparing the quality of the different proposed techniques, one needs graphs
with \emph{reference communities}, that is, communities known beforehand. Since
it is very difficult to have large real graphs with reference communities
(mainly because these would require a manual labeling), graphs for benchmarking
community detection algorithms are typically generated synthetically.

@@

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of different sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the fraction of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by obeying the described constraints.

### 2018-11-09 generators_streaming.tex
Fixed text to comply with plagiarism requirements

\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented an evaluation framework for linked stream data processing engines. The framework uses a data generator for the Stream Social network data Generator (S2Gen) that simulates what users continuously generate on their social network activities (e.g., posts) in addition to the  user metadata such as users' profile information, social network relationships, posts, photos and GPS information. The data generator of this framework provides the users the flexibility to control the characteristics of the generated data by tanning a range of parameters including the period in which the social activities are generated (generating period), the maximum number of posts/comments/photos for each user per week and the correlation probabilities between the different objects (e.g., users) in the social network.

\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced another framework for benchmarking RDF Stream Processing systems, RSPLab. The Streamer component of this framework is designed to publish RDF streams from the various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}). In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an open-source framework for publishing and sharing RDF streams on the Web~\cite{mauri2016triplewave}.   TripleWave acts as a mean for plugging-in diverse Web data sources and for consuming streams in both push and pull mode.

>>>>

\paragraph{S2Gen}  The streaming mode has mainly  attracted the attention of the
RDF and Semantic Web community. Thus, Phuoc et al.~\cite{le2012linked} presented
an evaluation framework for linked stream data processing engines. The framework
uses a datasets generated with the Stream Social network data Generator
(S2Gen), which 
simulates streams of user interactions (or events) in social networks 
(e.g., posts) in addition to the  user metadata such as users' profile
information, social network relationships, posts, photos and GPS information.
The data generator of this framework provides the users the flexibility to
control the characteristics of the generated stream by tanning a range of
parameters, which includes the frequency at which interactions are generated, 
limits such as the maximum number of messages per user
and week, and the correlation probabilities between the different objects (e.g.,
users) in the social network.

\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
another framework for benchmarking RDF Stream Processing systems, RSPLab. The
Streamer component of this framework is designed to publish RDF streams from the
various existing RDF benchmarks (e.g., BSBM, LUBM) (see Section~\ref{sec:generators_LinkedData}).
In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
open-source framework for publishing and sharing RDF streams on the
Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
and combining streams from multiple Web data sources, in both push and pull mode.
